\textbf{Analyzing Machupo virus-receptor binding by molecular dynamics simulations}

### 2014-01-06 paper.tex
Updated to fix 3 of the 4 remaining changes.

\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{lineno}

@@

Here we propose that much of these complexities can be avoided if all we are interested in is a relative comparison of the effects of different mutations on protein-protein interactions, rather than measuring an absolute or relative binding affinity with experimentally realistic units. We impart a pulling force within an all-atom molecular dynamics simulation on one member of the complex while the other is held in place. Then, we measure the force required for dissociation \citep{Gumbart2012,Lu1999,Park2004,Is2001A,Is2001B}. As a proxy for relative binding affinity, we use the maximum applied force required for separation and the area under the force-versus-distance curve (AUC). Although such biasing techniques are commonly used in protein-ligand binding problems, they are less commonly applied to protein--protein interactions, and almost never to mutational analysis in a protein--protein system. This is largely the result of free energy convergence difficulties and computational limitations \citep{Cuendet2008,Cuendet2011}; using maximum force or simple AUC can solve these problems. For comparison, we also calculate relative free energy differences using the traditional dual topology FEP paradigm, and we show that the two approaches yield congruent results.

@@

The hTfR1 is the primary receptor used by MACV for binding its host cell prior to infection. The primary role of hTfR1 $in~vivo$ is to bind transferrin for cellular iron uptake. The hTfR1 protein contains three extracellular domains: two basilar domains and an apical domain. The two basilar domains serve most of the transferrin-binding function \citep{Abraham2010,Rad20112}. Viral entry is initiated by GP1 binding to the apical domain of hTfR1. Previous work has indicated that the GP1/hTfR1 binding interaction is the primary determinant of MACV host range variation \citep{Rad20111,Rad20112}. The co-crystal structure shows the high affinity interaction between GP1 and hTfR1 forces the normally flexible loop in the apical domain of hTfR1 into a rigid $\beta$-pleated sheet domain. For GP1, several extended loops mediate binding to hTfR1 \citep{Abraham2010,Rad20112}, and many of the interface interactions are mediated by extensive hydrogen-bonding networks \citep{Abraham2010}. Experimental alanine-scanning and whole-cell infectivity assays have identified several sites in both GP1 and hTfR1 that are probably critical for establishing infection \citep{Rad20111,Rad20112}.

@@

NAMD was used for all simulations in this study \citep{Phillips2005}. In addition to the modeled system, for equilibration we generated a configuration file that fixed the $\alpha$-carbon backbone. This was accomplished by setting the B-factor column to 1 for the fixed atoms and to zero for all other atoms. Further, we generated a configuration file with fixed $\alpha$-carbon atoms at residues 41-92 (numbered linearly, in this case, starting at 1 for the first amino acid as was required for NAMD) in the hTfR1. The second file was used to affix a harmonic restraint, thus preventing any unfolding due to system reduction. More importantly, the harmonic restraint allowed the protein complex to equilibrate while preventing any drift from its predefined position; the restraint did not constrain the structure of each protein, or the relative position or orientation of the two proteins to each other. Finally, we calculated the system center and dimensions for use in molecular dynamics settings.

The exact NAMD configuration file is made available as a github repository with all necessary set up files is provided. We used the Charmm27 \citep{Brooks1983} all-atom force field. The initial system temperature was set to 310K. Several typical MD settings were used including switching and cutoff distances (see provided configuration files). In addition, we used a 2 femtosecond time step with rigid bonds. We used periodic boundary conditions with the particle mesh ewald (PME) method of computing full system electrostatics outside of the explicit box. Furthermore, we used a group pressure cell, flexible box, langevin barostat, and lavegin thermostat during equilibration. A harmonic restraint (called harmonic constraint in VMD) was set as stated previously.

@@

We used the final state from each equilibrated system to restart another MD simulation. Our steering protocol is fundamentally similar to \citet{Cuendet2008} with slightly different parameter choices. Perhaps the one significant difference lies in our choosing to not use a thermostat or barostat. We can make this choice because we are not trying to calculate the binding free energy by any physically rigorous approach (the Jarzynski inequality being one example). Following equilibration, the final state of each simulation was used to generate a configuration file fixing the $\alpha$-carbon on residues 1, 58, 73-83, 96, 136, 137, 138, and 161 (again with linear numbering) in the hTfR1. These residues were selected as they are far from the binding interface and sufficiently distributed to prevent any orientational motion of the receptor relative to the viral spike protein. The center of mass of the $\alpha$-carbons of all residues (163-318 in linear numbering) in GP1 received an applied force during the simulation. The NAMD convention does not actually apply a force to all $\alpha$-carbon atoms, but rather uses the selection to compute an initial center of mass. Then, during the steering run, the single center of mass point is pulled with the parameters desribed below. We used the same force field parameters (exclude, cutoff, switching, etc.), the same integrator parameters (time step, rigidbonds on, all molecular being wrapped, etc.), and the same particle mesh ewald parameters as in equilibration. Periodic boundary conditions were incorporated as part of the system (as is the convention in NAMD restart) and PME was again used to approximate full system electrostatics.

We ran test simulations at several force constants and visually inspected the results. A force constant of 5~kcal/mol/\AA$^2$ was chosen due to its relatively low signal-to-noise ratio. This constant is slightly lower than the more common 7~kcal/mol/\AA$^2$ found in several recent studies; that value is commonly selected primarily because it is the force constant found in the NAMD, SMD tutorial available through the developers. Moreover, the force constant could very likely be set to a range of nearby values with little loss in predictive power. In SMD experiments the pulling velocity should be as low as possible for the available computational time \citet{Cuendet2008,Cuendet2011}. Thus we choose a velocity of 0.000001~\AA/fs = 1~\AA/ns, and direction down the positive $z$-axis. This number could be set to pull faster if the computing time must be reduced, but slower than necessary pulling speeds are not typically considered problematic.

@@

Briefly, we used the traditional dual topology approach to FEP citep{Gao2006,Pearlman1994}. This involves a thermodynamic cycle where a set of atoms are progressively decoupled from the environment while another set of atoms are progressively coupled. To compute the relative free energy difference requires knowing the free energy change when the transformation is carried out for the bound complex and the individual protein. Then, one can compute the relative free energy difference between a WT and mutant complex by taking the difference between the energy required to decouple/couple the atoms in solution from the energy required to decouple/couple the atoms in the bound complex citep{Gao2006,Pearlman1994}.

Again, the NAMD configuration file is made available via github. We used a similar configuration to that in equilibration. One significant difference was to make a cubic water box with a side length equal to the long axis of the complex plus a 10~\AA\  buffer on either side, and simply restrict center of mass motion with the NAMD setting. This was done to avoid affecting the system energy while calculating free energy differences.

@@

The statistical package R was used for all further analysis and visualization. Each of the 50 independent trajectories per mutant produced a fairly noisy force curve. The force curves for each mutant were smoothed either by using the smooth.spline and predict functions in R with default settings over all replicates as in Figure~\ref{fig:force_curve}. The latter approach was used for statistical analysis. The two primary descriptive statistics we used were maximum interpolated applied force and total area under the interpolated curve (AUC). We used the pairwise.t.test function with the FDR p-value correction to test for significance. The ggplot \citep{ggplot} package was used to generate most of the figures.

@@

Despite the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. In the bound conformation, two sites of the loop have root mean squared fluctuation (RMSF) values in the top half of all receptor sites during equilibration (Figure~\ref{fig:rmsf}), and those are almost completely exposed to solvent. This is unsurprising considering the high degree of burial that occurs as a result of viral binding. Computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as to cause rapid unbinding. In fact, the RMSD over trajectory looks highly invariant across mutants (Figure~\ref{fig:rmsd}). By comparison to the equilibration RMSF calculation, near the end of the SMD trajectory all of the residues in the WT receptor interfacial strand are in the top half of RMSF over all receptor sites (Figure~\ref{fig:rmsf_comparison}). Thus, if sufficient simulation time is not dedicated to allowing this unfolding process, standard free energy techniques may miss the energetic contributions that result from ordering the flexible loop in the hTfR apical domain.

@@

We proceeded to analyze this system using two molecular dynamics techniques. First, in SMD by using a known force constant, and pulling with a constant velocity, we could calculate the applied force during protein--protein dissociation \citep{Cuendet2008,Cuendet2011}. A typical averaged force curve comparison can be seen in Figure~\ref{fig:force_curve}. As seen in Figure~\ref{fig:force_curve}, this distance was relatively consistent among mutants. The supplementary movie visually illustrates the separation distance between peptide domains. The quantities maximum applied force and AUC were derived from the force versus distances curves. Their summary statistics are reported in Table~\ref{tab:summary_statistics}. As we are more interested in the phenotypic impact of interface mutations we avoided many of the more physically rigorous, but technically complicated calculations that are possible with SMD \citep{Is2001A,Is2001B}.

@@

We proceeded to compare our SMD results to that of the standard dual topology FEP approach to calculate relative free energy differences. The correlation between the energetically rigorous FEP and our statistical approach is high. For all 11 complexes tested, the correlation between max force and FEP was $r=-0.795$ at $p=0.0034$ (Figure~\ref{fig:fep}), and the correlation between AUC and FEP was $r=-0.593$ at $p=0.055$. Because of this strong correlation, we refer exclusively to the SMD results for the remainder of this work.

We found that relative to WT, one alanine mutation (Tyr211Ala) produced a very large and statistically significant difference in the maximum applied force and AUC (Figure~\ref{fig:force_curve}, Table~\ref{tab:MAF_pairwise}), while the other two did not (Table~\ref{tab:MAF_pairwise}). When considering additional mutants (also discussed below), we found that maximum applied force was generally sufficient to distinguish mutants (Tables~\ref{tab:MAF_pairwise} and~\ref{tab:MAF_p}), and AUC was able to add a few more statistically significant differences (Table~\ref{tab:AUC_p}). In general, however, maximum applied force seemed to be the more sensitive statistic than AUC.

@@

Last, we further analyzed a single mutation in GP1, vArg111Ala. As mentioned in the previous subsection, in our simulations this mutant showed no significant change in either maximum applied force or AUC (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}), even though both quantities were, on average, lower than in WT (Table~\ref{tab:summary_statistics}). This result was somewhat surprising, since Tyr211Ala, presumably disrupting the same hydrogen-bonding network as vArg111Ala, displayed a significant reduction in affinity. To probe the interaction between position 111 in the GP1 and position 211 in the hTfR1 further, we also tested the double mutant vArg111Ala/Tyr211Ala. This double mutant showed affinity indistinguishable from WT and significantly higher than Tyr211Ala alone  (Table~\ref{tab:MAF_pairwise}). This result shows that the two sites do indeed interact, and that replacing the hydrogen-bonding network at these sites with a hydrophobic interaction could lead to comparable binding affinity.

@@

There are a few additional challenges for investigating host-virus interaction via molecular dynamics simulation. As with any atomistic simulation, there is going to be a fairly large noise to signal ratio. To reduce noise, one could further customize each simulation, e.g. by determining the optimal pulling speed. Furthermore, larger amounts of computational resources will have a direct and powerful impact on the strength of any atomistic study \citep{Shaw2012}. Such resources could come in the form of increased compute time, improved code, or customized hardware for floating point operations \citep{Shaw2011}. With improved resources, we could investigate thousands of individual permutations in the GP1/hTfR1 binding interface. In addition, with additional compute time it would be possible to incorporate equilibrium sampling approaches \citep{Buch2011} or use brute force equilibrium approaches \citep{Giorgino2012} to improve resolution.

For future studies, although our approach offers the simplicity of not requiring prior knowledge about a system of interest (other than a bound model), at this point SMD may not the best approach for many relative affinity calculations. To ensure one's results are independent of the dissociation path one selects would require computing the work of separation for all likely paths. Such an approach eventually requires using the Jarzynski inequality \citep{Jar1997} to establish a lower limit for binding energy and would quickly become computationally inefficient for evaluating a large number of mutations in most systems. However, considering the strong correlation between FEP and SMD in this system, it may not be important to ensure one's results are path independent for relative affinity calculations.

More importantly, with no \textit{a priori} knowledge of the appropriate number of equilibration samples, the best duration of equilibration, the appropriate number of pulling runs, or the best pulling speed means the computational expense in our SMD protocol may not be commensurate with the information provided. For example, another all atom approach that makes calculations via short simulations of spatially restrained complexes has proven capable of generating relatively accurate binding affinities with less compute time than is required from our steering strategy \citep{Gumbart2013,Gumbart2013b}. That being said, there is no reason to believe this SMD approach to mutagenic studies could not be optimized to reduce computational expense. Further analysis would be needed to understand the lower limits of resources required for accurate predictions.

\section{Acknowledgements}
This work was carried out using high-performance computing resources provided by the High Performance Computing Center (HPCC) at Texas Tech University at Lubbock \\ (http://www.hpcc.ttu.edu) and the Texas Advanced Computing Center (TACC) at The University of Texas at Austin (http://www.tacc.utexas.edu). The authors acknowledge Bryan Sutton for opening access to the Hrothgar cluster. The authors also acknowledge the reviewers Ilan Samish and Matteo Masetti for their helpful comments in preparing this manuscript.

\bibliographystyle{MBE}
\bibliography{paper}

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsfs.pdf}}
\caption{\label{fig:rmsf}\title{RMSF values during equilibration.} The RMSF values for every site in the bound complex computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. Indices 17-25 are the hTfR flexible loop. The plot shows the flexibility of each site is essentially independent of mutation, and two sites (indices 17 and 18) above 0.72~\AA\ are a part of the flexible loop in the free receptor. However, these two residues are not actually found in the protein--protein interface, but rather are almost completely solvent exposed with the virus bound.}
\end{figure}

>>>>

\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{color}

@@

Here we propose that much of these complexities can be avoided if all we are interested in is a relative comparison of the effects of different mutations on protein-protein interactions, rather than measuring an absolute or relative binding affinity with experimentally realistic units. We impart a pulling force within an all-atom molecular dynamics simulation on one member of the complex while the other is held in place. Then, we measure the force required for dissociation \citep{Gumbart2012,Lu1999,Park2004,Is2001A,Is2001B}. Although such biasing techniques are commonly used in protein-ligand binding problems, they are less commonly applied to protein--protein interactions, and almost never to mutational analysis in a protein--protein system. This is largely the result of free energy convergence difficulties and computational limitations \citep{Cuendet2008,Cuendet2011}. Using a proxy for relative binding affinity rather than caluclating absolute affinities can solve these problems. Here, as proxies, we use the maximum applied force required for separation and the area under the force-versus-distance curve (AUC). For comparison, we also calculate relative free energy differences using the traditional dual topology FEP paradigm, and we show that the two approaches yield congruent results.

@@

The hTfR1 is the primary receptor used by MACV for binding its host cell prior to infection. The primary role of hTfR1 $in~vivo$ is to bind transferrin for cellular iron uptake. The hTfR1 protein contains three extracellular domains: two basilar domains and an apical domain. The two basilar domains serve most of the transferrin-binding function \citep{Abraham2010,Rad20112}. Viral entry is initiated by GP1 binding to the apical domain of hTfR1. Previous work has indicated that the GP1/hTfR1 binding interaction is the primary determinant of MACV host range variation \citep{Rad20111,Rad20112}. The co-crystal structure shows that the high affinity interaction between GP1 and hTfR1 forces the normally flexible loop in the apical domain of hTfR1 into a rigid $\beta$-pleated sheet domain. For GP1, several extended loops mediate binding to hTfR1 \citep{Abraham2010,Rad20112}, and many of the interface interactions are mediated by extensive hydrogen-bonding networks \citep{Abraham2010}. Experimental alanine-scanning and whole-cell infectivity assays have identified several sites in both GP1 and hTfR1 that are probably critical for establishing infection \citep{Rad20111,Rad20112}.

@@

NAMD was used for all simulations in this study \citep{Phillips2005}. In addition to the modeled system, for equilibration we generated a configuration file that fixed the $\alpha$-carbon backbone. This was accomplished by setting the B-factor column to 1 for the fixed atoms and to zero for all other atoms. Further, we generated a configuration file with fixed $\alpha$-carbon atoms at residues 41-92 (numbered linearly, in this case, starting at 1 for the first amino acid as was required for NAMD) in the hTfR1. The second file was used to affix a harmonic restraint, thus preventing any unfolding due to system reduction. More importantly, the harmonic restraint allowed the protein complex to equilibrate while preventing any drift from its predefined position; the restraint did not constrain the structure of each protein, or the relative position or orientation of the two proteins to each other. Finally, we calculated the system center and dimensions for use in molecular dynamics settings. The exact NAMD configuration files are available on github (https://github.com/clauswilke/MACV\_SMD).

We used the Charmm27 \citep{Brooks1983} all-atom force field. The initial system temperature was set to 310K. Several typical MD settings were used including switching and cutoff distances (see provided configuration files). In addition, we used a 2 femtosecond time step with rigid bonds. We used periodic boundary conditions with the particle mesh ewald (PME) method of computing full system electrostatics outside of the explicit box. Furthermore, we used a group pressure cell, flexible box, langevin barostat, and lavegin thermostat during equilibration. A harmonic restraint (called harmonic constraint in VMD) was set as stated previously.

@@

We used the final state from each equilibrated system to restart another MD simulation. Our steering protocol is fundamentally similar to \citet{Cuendet2008} with slightly different parameter choices. Perhaps the one significant difference lies in our choosing to not use a thermostat or barostat. We can make this choice because we are not trying to calculate the binding free energy by any physically rigorous approach (the Jarzynski inequality being one example). Following equilibration, the final state of each simulation was used to generate a configuration file fixing the $\alpha$-carbon on residues 1, 58, 73-83, 96, 136, 137, 138, and 161 (again with linear numbering) in the hTfR1. These residues were selected as they are far from the binding interface and sufficiently distributed to prevent any orientational motion of the receptor relative to the viral spike protein. The center of mass of the $\alpha$-carbons of all residues (163-318 in linear numbering) in GP1 received an applied force during the simulation. The NAMD convention does not actually apply a force to all $\alpha$-carbon atoms but rather uses the selection to compute an initial center of mass. Then, during the steering run, the single center of mass point is pulled with the parameters desribed below. We used the same force field parameters (exclude, cutoff, switching, etc.), the same integrator parameters (time step, rigidbonds on, all molecular being wrapped, etc.), and the same particle mesh ewald parameters as in equilibration. Periodic boundary conditions were incorporated as part of the system (as is the convention in NAMD restart) and PME was again used to approximate full system electrostatics.

We ran test simulations at several force constants and visually inspected the results. A force constant of 5~kcal/mol/\AA$^2$ was chosen due to its relatively low signal-to-noise ratio. This constant is slightly lower than the more common 7~kcal/mol/\AA$^2$ found in several recent studies; that value is commonly selected primarily because it is the force constant found in the SMD tutorial available through the NAMD  developers. Moreover, the force constant could very likely be set to a range of nearby values with little loss in predictive power.

In SMD experiments the pulling velocity should be as low as possible for the available computational time \citep{Cuendet2008,Cuendet2011}. We choose a velocity of 0.000001~\AA/fs = 1~\AA/ns, and direction down the positive $z$-axis. One could use faster pulling if the computing time must be reduced, but slower than necessary pulling speeds are not typically considered problematic.

@@

Briefly, we used the traditional dual topology approach to FEP \citep{Gao2006,Pearlman1994}. This involves a thermodynamic cycle where a set of atoms are progressively decoupled from the environment while another set of atoms are progressively coupled. To compute the relative free energy difference requires knowing the free energy change when the transformation is carried out for the bound complex and the individual protein. Then, one can compute the relative free energy difference between a WT and mutant complex by taking the difference between the energy required to decouple/couple the atoms in solution from the energy required to decouple/couple the atoms in the bound complex \citep{Gao2006,Pearlman1994}.

Again, the NAMD configuration file is made available via github \\ (https://github.com/clauswilke/MACV\_SMD). We used a similar configuration to that in equilibration. One significant difference was to make a cubic water box with a side length equal to the long axis of the complex plus a 10~\AA\  buffer on either side, and simply restrict center of mass motion with the NAMD setting. This was done to avoid affecting the system energy while calculating free energy differences.

@@

The statistical package R was used for all further analysis and visualization. Each of the 50 independent trajectories per mutant produced a fairly noisy force curve. The force curves for each mutant were smoothed by using the smooth.spline() and predict() functions in R with default settings over all replicates as in Figure~\ref{fig:force_curve}. The two primary descriptive statistics we used were maximum interpolated applied force and total area under the interpolated curve (AUC). We tested for signifiant differences in maximum force or AUC by carrying out t tests for all pairwise combinations (each mutant compared to each other mutant), using the pairwise.t.test() function in R. We adjusted p values to correct for multiple testing using the False-Discovery-Rate (FDR) method \citep{BenjaminiHochberg1995}. The ggplot \citep{ggplot} package was used to generate most of the figures.

Analysis scripts and final data (except MD trajectories) are available on the github repository accompanying this publication (https://github.com/clauswilke/MACV\_SMD).

@@

Despite the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. In the bound conformation, only two sites of the loop have root mean squared fluctuation (RMSF) values in the top half of all receptor sites during equilibration (Figure~\ref{fig:rmsf}), and those are almost completely exposed to solvent. This is unsurprising considering the high degree of burial that occurs as a result of viral binding. Computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as to cause rapid unbinding. In fact, the RMSD over trajectory looks highly invariant across mutants (Figure~\ref{fig:rmsd}). In the unbound state, calculated near the end of the SMD trajectory, all of the residues in the WT receptor interfacial strand are in the top half of RMSF over all receptor sites (Figure~\ref{fig:rmsf_comparison}). Thus, if sufficient simulation time is not dedicated to allowing this unfolding process, standard free energy techniques may miss the energetic contributions that result from ordering the flexible loop in the hTfR apical domain.

@@

We analyzed the GP1/hTfR1 system using two molecular dynamics techniques. First, by carrying out SMD using a known force constant and pulling with a constant velocity, we could calculate the applied force during protein--protein dissociation \citep{Cuendet2008,Cuendet2011}. A typical averaged force curve comparison can be seen in Figure~\ref{fig:force_curve}. As seen in Figure~\ref{fig:force_curve}, the dissociation distance was relatively consistent among mutants. {\color{red}\emph{I would still like to see an array of figures with all averaged force curves.}} The supplementary movie visually illustrates the separation distance between peptide domains. The quantities maximum applied force and AUC were derived from the force-versus-distances curves. Their summary statistics are reported in Table~\ref{tab:summary_statistics}. As we are more interested in the phenotypic impact of interface mutations we avoided many of the more physically rigorous, but technically complicated calculations that are possible with SMD \citep{Is2001A,Is2001B}.

@@

We proceeded to compare our SMD results to that of the standard dual topology FEP approach to calculate relative free energy differences. The correlation between the energetically rigorous FEP and our statistical approach is high. For all 11 complexes tested, the correlation between max force and FEP was $r=-0.795$ at $p=0.0034$ (Figure~\ref{fig:fep}), and the correlation between AUC and FEP was $r=-0.593$ at $p=0.055$. Because of the strong correlation, we refer exclusively to the SMD results for the remainder of this work, focusing primarily on max force.

We found that relative to WT, one alanine mutation (Tyr211Ala) produced a very large and statistically significant difference in the maximum applied force and AUC (Figure~\ref{fig:force_curve}, Table~\ref{tab:MAF_pairwise}), while the other two did not (Table~\ref{tab:MAF_pairwise}). When considering additional mutants (also discussed below), we found that maximum applied force was generally sufficient to distinguish mutants (Tables~\ref{tab:MAF_pairwise} and~\ref{tab:MAF_p}), and AUC was able to add a few more statistically significant differences (Table~\ref{tab:AUC_p}). In general, however, and consistent with the FEP results, maximum applied force seemed to be the more sensitive statistic than AUC.

@@

Last, we further analyzed a single mutation in GP1, vArg111Ala. As mentioned previously, in our simulations this mutant showed no significant change in either maximum applied force or AUC (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}), even though both quantities were, on average, lower than in WT (Table~\ref{tab:summary_statistics}). This result was somewhat surprising, since Tyr211Ala, presumably disrupting the same hydrogen-bonding network as vArg111Ala, displayed a significant reduction in affinity. To probe the interaction between position 111 in the GP1 and position 211 in the hTfR1 further, we also tested the double mutant vArg111Ala/Tyr211Ala. This double mutant showed affinity indistinguishable from WT and significantly higher than Tyr211Ala alone  (Table~\ref{tab:MAF_pairwise}). This result shows that the two sites do indeed interact, and that replacing the hydrogen-bonding network at these sites with a hydrophobic interaction could lead to comparable binding affinity.

@@

There are a few additional challenges for investigating host-virus interactions via molecular dynamics simulation. As with any atomistic simulation, there is going to be a fairly large noise-to-signal ratio. To reduce noise, one could further customize each simulation, e.g. by determining the optimal pulling speed. Furthermore, larger amounts of computational resources will have a direct and powerful impact on the strength of any atomistic study \citep{Shaw2012}. Such resources could come in the form of increased compute time, improved code, or customized hardware for floating point operations \citep{Shaw2011}. With improved resources, we could investigate thousands of individual permutations in the GP1/hTfR1 binding interface. In addition, with additional compute time it would be possible to incorporate equilibrium sampling approaches \citep{Buch2011} or use brute force equilibrium approaches \citep{Giorgino2012} to improve resolution.

For future studies, although our approach offers the simplicity of not requiring prior knowledge about a system of interest (other than a bound model), at this point SMD may not the best approach for many relative affinity calculations. To ensure one's results are independent of the dissociation path one selects would require computing the work of separation for all likely paths. Such an approach eventually requires using the Jarzynski inequality \citep{Jar1997} to establish a lower limit for binding energy and would quickly become computationally inefficient for evaluating a large number of mutations in most systems. However, considering the strong correlation between FEP and SMD in this system, it may not be important to ensure one's results are path independent for relative affinity calculations, as long as the same path is used for all complexes.

More importantly, with no \textit{a priori} knowledge of the appropriate number of equilibration samples, the best duration of equilibration, the appropriate number of pulling runs, or the best pulling speed means the computational expense in our SMD protocol may not be commensurate with the information provided. For example, another all atom approach that makes calculations via short simulations of spatially restrained complexes has proven capable of generating relatively accurate binding affinities with less compute time than is required from our steering strategy \citep{Gumbart2013,Gumbart2013b}. That being said, there is no reason to believe this SMD approach to mutagenic studies could not be optimized to reduce computational expense. Further analysis will be needed to understand the lower limits of resources required for accurate predictions.

\section{Acknowledgements}
This work was carried out using high-performance computing resources provided by the High Performance Computing Center (HPCC) at Texas Tech University at Lubbock \\ (http://www.hpcc.ttu.edu) and the Texas Advanced Computing Center (TACC) at The University of Texas at Austin (http://www.tacc.utexas.edu). We would like to thank Bryan Sutton for opening access to the Hrothgar cluster and the reviewers Ilan Samish and Matteo Masetti for their helpful comments on this work.

\bibliographystyle{peerj}
\bibliography{paper}

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsfs.pdf}}
\caption{\label{fig:rmsf}\title{RMSF values during equilibration.} The RMSF values for every site in the bound complex computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. Indices 17-25 are the hTfR flexible loop. The plot shows the flexibility of each site is essentially independent of mutation, and two sites (indices 17 and 18) above 0.72~\AA\ are a part of the flexible loop in the free receptor. However, these two residues are not actually found in the protein--protein interface, but rather are almost completely solvent exposed with the virus bound. {\color{red}\emph{Please highlight the flexible loop, as in Fig. 4.}}}
\end{figure}
